  %-------------------------------------------------------------------------------
  %	SECTION TITLE
  %-------------------------------------------------------------------------------
  \cvsection{Experience}
  %-------------------------------------------------------------------------------
  %	CONTENT
  %-------------------------------------------------------------------------------

  \begin{cventries}

  %---------------------------------------------------------
    \cventry
    {Principal Software Engineer {\enskip\textendash\enskip} Product Technical Strategy} % Job title
    {Tanium} % Organization
    {Morrisville, NC - Hybrid} % Location
    {Dec. 2022 - Present} % Date(s)
    {
      \begin{cvitems}
        \item Founded and lead the Product Technical Strategy Team at Tanium after identifying a gap in communication between Product Management and Engineering
        \item Identify technical patterns across R\&D, and formalize solutions and guidelines for all of engineering.
        \item Engage in complex customer escalations
        \item Serve as architect for projects that span the entire Engineering organization
      \end{cvitems}
    }

    \cventry
      {Staff Software Engineer \enskip\textendash\enskip Platform} % Job title
      {} % Organization
      {} % Location
      {Mar. 2021 - Dec. 2022} % Date(s)
      {
        \begin{cvitems}
          \item Working on native extensions to the Tanium Client for products such as Tanium Recorder, Stream, and Threat Response
          \item Lead development of strategic initiatives across the R\&D organization
          \item Lead an effort to reduce the footprint of the Tanium Client across our customer base, focusing on CPU, memory, and IO reductions
        \end{cvitems}
      }

    \cventry
      {Senior Software Engineer \enskip\textendash\enskip Threat Response} % Job title
      {} % Organization
      {} % Location
      {Jun. 2019 - Mar. 2021} % Date(s)
      {
        \begin{cvitems}
          \item Helped launch a new endpoint extension to the Tanium Client: Tanium Stream. Stream allows customers to use Tanium to send endpoint telemetry directly to any datalake
          \item Helped with the launch of Threat Response 2.0, a major change to the Threat Response product
          \item Created a monorepo for endpoint extensions and facilitated adoption across the Endpoint team
        \end{cvitems}
      }

    \cventry
      {Developer Team Lead / Senior Software Engineer \enskip\textendash\enskip QRadar Advisor with Watson} % Job title
      {IBM} % Organization
      {Raleigh, NC - Hybrid} % Location
      {Jul. 2018 - Jun. 2019} % Date(s)
      {
        \begin{cvitems}
          \item Served as senior team architect for on-premises and cloud products for Cybersecurity
          \item Advised development team of 15 developers and oversaw day-to-day work. Aligned team's work with Product Management and Engineering Management objectives
        \end{cvitems}
      }
      
    \cventry
      {Developer Team Lead / Advisory Software Engineer \enskip\textendash\enskip QRadar Advisor with Watson} % Job title
      {} % Organization
      {} % Location
      {Jul. 2017 - Jul. 2018} % Date(s)
      {
        \begin{cvitems}
          \item Lead team building cybersecurity applications on top of the QRader SIEM
          \item Promoted to advise development team of 15 developers and oversaw day-to-day work
        \end{cvitems}
      }

    \cventry
      {Staff Software Engineer \enskip\textendash\enskip QRadar Advisor with Watson}
      {}
      {Atlanta, GA - Onsite} % Location
      {Apr. 2016 - Jun. 2017}
      {
        \begin{cvitems}
          \item Created the QRadar Application dockerized build framework and oversaw implementation for other apps
        \end{cvitems}
      }
              
    \cventry
      {Software Engineer \enskip\textendash\enskip X-Force Threat Intelligence \& IDS/IPS Development}
      {}
      {} % Location
      {May. 2014 - Apr. 2016}
      {
      \begin{cvitems}
        \item Improved production system uptime to 99.9\% as the sole North American Systems Operations Engineer
      \end{cvitems}
      }

    \cventry
      {Security Software Intern \enskip\textendash\enskip X-Force Threat Intelligence}
      {}
      {} % Location
      {May 2013 - May 2014}
      {
      \begin{cvitems}
        \item Worked on targeted research and software solutions within the IBM X-Force QA Team
        \item Rewrote the front-end and back-end of a global security research sensor network in latest language stacks
      \end{cvitems}
      }

  %---------------------------------------------------------
    \cventry
      {Resident Advisor}
      {University of Virginia}
      {Charlottesville, VA, USA}
      {Aug. 2012 - May 2014}
      {
        \begin{cvitems}
          \item Planned programs and facilitated academic integrity for 36 residents over two academic years
        \end{cvitems}
      }

  %---------------------------------------------------------
    \cventry
      {IT Development Associate}
      {Implus Footcare, LLC}
      {}
      {Aug. 2011 - Aug. 2012}
      {
        \begin{cvitems}
          \item Developed targeted modular projects for centralized data organization for company intranet
        \end{cvitems}
      }

    \cventry
    {IT Department Intern}
    {}
    {}
    {Summer 2009, 2010, 2011}
    {
      \begin{cvitems}
        \item Modernized company intranet code, integrated Active Directory
      \end{cvitems}
    }
  %---------------------------------------------------------

  \end{cventries}
